Dynein project log

### 2017-03-01 thesis_stuff/thesis_stuff.tex

\subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
Takahide Kon, Kenji Imamula, Anthony J Roberts, Reiko Ohkura, Peter J Knight, I R Gibbons, Stan A Burgess & Kazuo Sutoh\\
Discuss how other work has shown that MT affinity is controlled by registry. They do this study in vivo, and show that there is a coupling between ATPase activity and MT binding which is destroyed by locking the coiled coils into registries.

@@

>>>>

\subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
Takahide Kon, Kenji Imamula, Anthony J Roberts, Reiko Ohkura, Peter J Knight, I R Gibbons, Stan A Burgess \& Kazuo Sutoh\\
Discuss how other work has shown that MT affinity is controlled by registry. They do this study in vivo, and show that there is a coupling between ATPase activity and MT binding which is destroyed by locking the coiled coils into registries.

@@

\textbf{The supplemental movies could be used in a presentation, along with the molecular dynamics simulations in the MTBD-MT complex paper.}
